---
title: "Overview of Evaluation Methods"
author: "Ernest Guevarra"
date: "21 January 2020" #'`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
mono_light(
  base_color = "#002147",
  title_slide_background_image = "",
  title_slide_background_size = "cover",
  header_font_google = google_font("Fira Sans"),
  text_font_google   = google_font("Fira Sans Condensed"),
  text_font_size = "1.2em",
  code_font_google   = google_font("Fira Mono"),
  text_slide_number_font_size = "0.5em"
)
```

class: inverse, center, middle

`r fontawesome::fa("envelope", fill = "white")` ernest@guevarra.io

`r fontawesome::fa("globe", fill = "white")` ernest.guevarra.io

`r fontawesome::fa("linkedin", fill = "white")` ernestguevarra

---

# Structure of lecture

* Three case studies (one per hour)

In each case study:

* Examine the various considerations for evaluation

* Discuss the possible methods to use for evaluation and their pros and cons

At the end:

* Recap and summarise methods used for evaluation

---

class: inverse, center, middle

## Case Study 1

## Coverage assessment of direct nutrition interventions in Liberia

---

# Background

* On 3 February 2014, the Republic of Liberia joined the Scaling Up Nutrition (SUN) Movement

* Liberia had developed a National Nutrition Policy which was designed to complement and strengthen actions set out in the Nutrition Health Policy and the Food Security and Nutrition Strategy

* Liberia's 2012 Poverty Reduction Strategy (PRS) had also identified nutrition as a national priority and an integral element of the overall development agenda

---
